---
title: "Project BOSTON"
author: "YU SUN & LIYU QIANG"
date: "2/24/2019"
output:
  html_document:
    df_print: paged
---
# first project 
# Boston Crime
# Goals
#1. summary each year total crime number,total crime number in each district and find top 3 dangerous district in Boston. 
#2.Seperate 24 hours to three 8-hours periods, 8am-16pm, 17pm-24am, 1am-7am. Compare the crime number happening in each periods in top 3 dangerous districts with the crime number distribution in Boston 
#3.Compared the crime group happening in each period in Boston and top 3 dangerous districts

```{r}
crime<-read.csv("/Users/fudanvip/IE7280/project1/test/dataset/bostoncrime.csv",sep = ",",stringsAsFactors = FALSE)
library(ggplot2)
library(dplyr)
year_crime<-summarise(group_by(crime,year),total_number_of_crime_each_year=n())
year_crime
ggplot(crime, aes(x = year)) +geom_histogram(binwidth = 1, color = "grey30", fill = "grey")+theme_bw()+ylab("total crime number")
any(crime$district=="")
crime_district<-filter(crime, district != "")
district<-summarise(group_by(crime_district,district),total_number_of_crime=n())
district
top_district_total<-arrange(district,desc(total_number_of_crime))[1:3,]
top_district_total
top_district_total$district
library(magrittr)
district_year<-crime_district %>%
  group_by(year,district)%>%
  summarise(total_crime=n()) %>%
  arrange(year,desc(total_crime)) %>%
  mutate(rank=row_number())
district_year
top3<-filter(district_year, rank <=3)
top3
```
## the top3 high crime district in each year are the same as the top3 total high crime district from 2015-2019
```{r}
ggplot(top3,aes(x=year,y=total_crime,fill=factor(district)))+
  geom_bar(stat="identity",position="dodge")+ylab("crime number")+
  xlab("year")
year2015<-filter(crime,year==2015)
unique(year2015$month)
```
# so the data for year 2015 is not complete. and the data for 2019 also is not completed. this the reason why 
# the total number of crime for 2015 and 2019 are much lower than other three year.
# we only have the code in district part. We do not know where the district is since we lack this information. Thus, we decide to use data in 2018 year to estimate where are top 3 dangerous district 
# take sample which is year == 18 and sample size = 5000. 
# we estimate the top 3 dangerous district are the part highlighted in yellow in the map.
```{r}
library("leaflet")
library("data.table")
library("sp")
library("rgdal")
library("KernSmooth")
library("dplyr")
library("ggplot2")
crime<-read.csv("/Users/sunyu/Desktop/IE 6600/bostoncrime.csv",sep = ",",stringsAsFactors = FALSE)
crime<- filter(crime,crime$long>-72)
crime<-filter(crime,crime$lat>41)
crime_s<- filter(crime,year==2018)
set.seed(1)
samp <- sample_n(crime_s, 5000)
setnames(samp, tolower(colnames(samp)))
samp<-as.data.table(samp, keep.rownames=FALSE, sorted=TRUE, value.name="value", na.rm=TRUE)
samp <- samp[!is.na(long)]
samp<- samp[!is.na(lat)]
kde <- bkde2D(samp[ , list(long,lat)],
              bandwidth=c(.0045, .0068), gridsize = c(100,100))
CL <- contourLines(kde$x1 , kde$x2 , kde$fhat)
LEVS <- as.factor(sapply(CL, `[[`, "level"))
NLEV <- length(levels(LEVS))
pgons <- lapply(1:length(CL), function(i)
  Polygons(list(Polygon(cbind(CL[[i]]$x, CL[[i]]$y))), ID=i))
spgons = SpatialPolygons(pgons)
# plot desity
leaflet(spgons) %>% addTiles() %>% 
  addPolygons(color = heat.colors(NLEV, NULL)[LEVS])
#plot circle on it
leaflet(spgons) %>% addTiles() %>%
  addPolygons(color = heat.colors(NLEV, NULL)[LEVS]) %>%
  addCircles(lng = samp$long, lat = samp$lat,
             radius = .01, opacity = .2, col = "blue")
```

# Period analysis 
# Vehicle Accident Response and Medical Assistance both are in Top 5 most happening crimes in each period for boston and Top 3 dangerous district
# We still can see the top 5 most happening crimes in 3 most dangerous district are different from Boston during each period. In top 3 dangerous district, the assault crimes are more common during night and late night.
```{r}
crime_district$period[crime_district$hour >=8 & crime_district$hour<=16 ]<-"Day" 
crime_district$period[crime_district$hour >16 | crime_district$hour ==0 ]<-"Night"
crime_district$period[crime_district$hour >=1 & crime_district$hour <8 ]<-"LateNight"
Time<-summarise(group_by(crime_district,period),total_crime=n())
TimeAndCrime<-crime_district %>%
  group_by(period,offense_code_group)%>%
  summarise(total_crime=n()) %>%
  arrange(period,desc(total_crime)) %>%
  mutate(rank=row_number())
top5<-filter(TimeAndCrime, rank <=5)
ptime1<-ggplot(top5, aes(x=factor(period), y=factor(offense_code_group), fill=total_crime)) + 
  xlab("oeriod")+ylab("crime code")+geom_tile()+ggtitle("boston time and crime")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
p1<-ggplot( Time, aes(x=period, y=total_crime,group=1))+geom_line(color="blue")+theme_bw()+xlab("boston period") 

top_district<-filter(crime_district,district %in% top_district_total$district)
TimeAndCrime2<-top_district %>%
  group_by(period,offense_code_group)%>%
  summarise(total_crime=n()) %>%
  arrange(period,desc(total_crime)) %>%
  mutate(rank=row_number())
top52<-filter(TimeAndCrime2, rank <=5)
ptime2<-ggplot(top52, aes(x=factor(period), y=factor(offense_code_group), fill=total_crime)) + 
  xlab("oeriod")+ylab("crime code")+geom_tile()+ggtitle("top3 district time and crime")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
Time2<-summarise(group_by(top_district,period),total_crime=n())
p2<-ggplot( Time2, aes(x=period, y=total_crime,group=1))+geom_line(color="red")+theme_bw()+xlab("top3 period")
library(gridExtra)
grid.arrange(p1, p2,ncol = 2)
grid.arrange(ptime1, ptime2,ncol = 2)
```
